---
title: "Business Intelligence Project"
author: 135230 Peter David Aringo 4.2B
date: "27/11/2023"
output:
  github_document:
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
editor_options:
  chunk_output_type: console
---

# Student Details

+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Student ID Number and Name**                    |   135230 - B - Peter Aringo                                                                                                                                              |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Course Code**                                   | BBT4206                                                                                                                                                                  |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Course Name**                                   | Business Intelligence II                                                                                                                                                 |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Program**                                       | Bachelor of Business Information Technology                                                                                                                              |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Semester Duration**                             | 21^st^ August 2023 to 28^th^ November 2023                                                                                                                               |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+

# Setup Chunk

We start by installing all the required packages

```{r Install Packages, echo=TRUE, message=FALSE, warning=FALSE}
if (!requireNamespace("renv", quietly = TRUE)) {
  install.packages("renv", dependencies = TRUE)
}
library(renv)

if (!requireNamespace("languageserver", quietly = TRUE)) {
  install.packages("languageserver", dependencies = TRUE)
}
library(languageserver)

if (!requireNamespace("readr", quietly = TRUE)) {
  install.packages("readr", dependencies = TRUE)
}
library(readr)

if (!requireNamespace("Amelia", quietly = TRUE)) {
  install.packages("Amelia", dependencies = TRUE)
}
library(Amelia)

if (!requireNamespace("ggcorrplot", quietly = TRUE)) {
  install.packages("ggcorrplot", dependencies = TRUE)
}
library(ggcorrplot)
if (!requireNamespace("e1071", quietly = TRUE)) {
  install.packages("e1071", dependencies = TRUE)
}
library(e1071)
if (!requireNamespace("caret", quietly = TRUE)) {
  install.packages("caret")
}
library(caret)
if (!requireNamespace("corrplot", quietly = TRUE)) {
  install.packages("corrplot")
}
library(corrplot)
# Install and load the 'ipred' package
if (!requireNamespace("ipred", quietly = TRUE)) {
  install.packages("ipred", dependencies = TRUE)
}
library(ipred)#
# Install and load the 'earth' package
if (!requireNamespace("earth", quietly = TRUE)) {
  install.packages("earth", dependencies = TRUE)
}
library(earth)
# Install and load the 'randomForest' package
if (!requireNamespace("randomForest", quietly = TRUE)) {
  install.packages("randomForest", dependencies = TRUE)
}
library(randomForest)
install.packages("SuperLearner")
library(SuperLearner)
install.packages("caretEnsemble")
library(caretEnsemble)
library(boot)
```

------------------------------------------------------------------------

**Note:** the following "*KnitR*" options have been set as the defaults in this markdown:\
`knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE, collapse = FALSE, tidy.opts = list(width.cutoff = 80), tidy = TRUE)`.

More KnitR options are documented here <https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html> and here <https://yihui.org/knitr/options/>.

```{r setup, echo=TRUE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
	eval = TRUE,
	echo = TRUE,
	warning = FALSE,
	collapse = FALSE,
	tidy = TRUE
)
```

------------------------------------------------------------------------

**Note:** the following "*R Markdown*" options have been set as the defaults in this markdown:

> output:\
> \
> github_document:\
> toc: yes\
> toc_depth: 4\
> fig_width: 6\
> fig_height: 4\
> df_print: default\
> \
> editor_options:\
> chunk_output_type: console

# 

```{r Load Dataset}

```

